### 2024-11-22 paper/overview.tex
Add ex env
Minor update
Minor fix

% AL
Additionally, SpecTec introduces another imperative language, \textit{AL}, for
the prose notation.
In AL, semantics are expressed algorithmically, in the form of step-by-step
instructions that take inputs and perform operations, mirroring the prose notation.
SpecTec translates declarative definitions in the DSL into algorithmic
definitions in AL.
The AL code below is the specification for the \texttt{testop} instruction
generated from the DSL:
\begin{lstlisting}[style=al]
@\textbf{Step\_pure/testop}@ nt testop {
    Assert (check_type_of_stack_top(nt))
    Pop (CONST nt c_1)
    Let c = @$\dollarcode$@testop_(nt, testop, c_1)
    Push (CONST I32 c)
}
\end{lstlisting}
Using AL, SpecTec generates reStructuredText code.
\cref{fig:spectec-testop} shows the generated document for \texttt{testop}
instruction.
The generated document closely resembles the official document except for some
minor notation changes and some missing hyperlinks.

>>>>

% AL
Additionally, SpecTec introduces another imperative language, \textit{AL}, for
representing the prose notation.
In AL, semantics are expressed algorithmically, in the form of step-by-step
instructions that take inputs and perform operations.
SpecTec translates declarative definitions in the DSL into algorithmic
definitions in AL.
The following code is generated from the DSL, illustrating the algorithmic
specification for the \texttt{testop} instruction using AL:
\begin{lstlisting}[style=al]
@\textbf{Step\_pure/testop}@ nt testop {
    Assert (check_type_of_stack_top(nt))
    Pop (CONST nt c_1)
    Let c = @$\dollarcode$@testop_(nt, testop, c_1)
    Push (CONST I32 c)
}
\end{lstlisting}
Using AL, SpecTec generates reStructuredText code.
\cref{fig:spectec-testop} shows the generated document for \texttt{testop}
instruction.
The generated document closely resembles the official document except for some
minor notation changes and some missing hyperlinks.
